Pillar 2 - Topic Modeling

### 2019-03-13 Pillar 2 - Topic Modeling.Rmd

@@

  mutate(
    TM_overview = n_topic %>% map( .f = my_LDA, corpus = d_cast$overview),
    TM_manual   = n_topic %>% map( .f = my_LDA, corpus = d_cast$manuals)
  )
```
##Model Evaluation
###Perplexity
Perplexity is a measure of how well a probability model predicts a sample. Thus we need to do cross validation. 
```{r}

@@

#Get perplexity
topic_test <- topic_model %>%
  mutate(perplex_overview = map(.x = TM_overview, .f = my_perplexity, d_cast$overview),
         perplex_manual   = map(.x = TM_manual,   .f = my_perplexity, d_cast$manual))
```
###log_likelihood
```{r useless stuff}
#Useless stuff:

my_loglike <- function(model){
  return(model@loglikelihood)
}
topic_test %>% mutate(loglike_overview = map(.x = TM_overview, .f = my_loglike)) %>% select(n_topic, loglike_overview)

  for( i in 1:length(topic_model$TM_overview)){
    tmp <- 
  }
}

lL <- list()
for(i in 1:length(topic_model$n_topic)){

  tmp <- topic_model$TM_overview[i]
  lL[[paste("n", 2*i)]] <- tmp[[1]]@loglikelihood

test1[[1]]@loglikelihood

log_like <- logLik(test1[[1]])

```
##Get Beta/Gamma functions
```{r getting gamma and beta, eval = TRUE}
get_beta <- function(results){

>>>>

#cross-validate
cross_validate <- function(my_dtm){
  #Number of documents (D)
  D <- nrow(my_dtm)

  #Assign documents to a fold
  folding <- sample(rep(1:10, ceiling(D))[seq_len(D)])

  for(k in n_topics) {
    for(chain in 1:10){
      train_set <- my_dtm[folding != chain, ]
      test_set  <- my_dtm[folding == chain, ]

      training <- my_LDA(k, train_set)
      testing  <- my_LDA(k, train_set)
    }
  }
}

@@

  mutate(
    TM_overview = n_topic %>% map( .f = my_LDA, corpus = d_cast$overview),
    TM_manual   = n_topic %>% map( .f = my_LDA, corpus = d_cast$manuals)
  )
```

##Model Evaluation
###Perplexity
Perplexity is a measure of how well a probability model predicts a sample. Thus we need to do cross validation. 
```{r}

@@

#Get perplexity
topic_test <- topic_model %>%
  mutate(perplex_overview = map(.x = TM_overview, .f = my_perplexity, d_cast$overview),
         perplex_manual   = map(.x = TM_manual,   .f = my_perplexity, d_cast$manual))
```

###log_likelihood
```{r useless stuff}
# #my_loglikelihood function
# my_loglike <- function(model){
#   return(model@loglikelihood)
# }
# 
# #get loglikelihood
# test2 <- topic_test %>% mutate(loglike_overview    = map(.x = TM_overview, .f = my_loglike),
#                                   loglike_manual   = map(.x = TM_manual,   .f = my_loglike))

#Log likelihood:
test3 <- topic_test %>% mutate(logLik_overview = map(.x = TM_overview, .f = logLik),
                               logLik_manual   = map(.x = TM_manual,   .f = logLik))

###Plots
```{r}
#perplexity
plot(topic_test$n_topic, topic_test$perplex_overview)
plot(topic_test$n_topic, topic_test$perplex_manual)

#log likelihood
plot(test3$n_topic, test3$logLik_overview)
plot(test3$n_topic, test3$logLik_manual)
```

##Get Beta/Gamma functions
```{r getting gamma and beta, eval = TRUE}
get_beta <- function(results){
